eag

### 2024-03-24 qmd/projects/msu-masters/wss/eag.qmd
commit for 3/20
commit updated url for website

```{r, echo = F}
eag <-
  read_excel("xlsx files/eag.xlsx", sheet = "test eag")

fid <-
  read_excel("xlsx files/eag.xlsx", sheet = "Peak")

@@

fid_plot <- 
filled_data %>%
  dplyr::select(MeasRetTime, Area, Height) %>%
  mutate(Height = ifelse(MeasRetTime < 3.2, 0, Height))
  # ggplot() +
  # geom_point(aes(x = MeasRetTime, y = Height)) +
  # geom_line(aes(x = MeasRetTime, y = Height)) +
  # theme_bw()
eag_plot <-
eag %>%
  mutate(row_num = row_number()) %>%
  rename("EAD" = 'EAD 1') 
ggplotly(
ggplot() +
  geom_line(data = fid_plot, aes(x = MeasRetTime, 
                                 y = Height), 
            color = "red") +
  geom_line(data = eag_plot, aes(x = scale_values(row_num)+1.2, 
                                 y = EAD * 100), 
            color = "blue") +

@@

>>>>

```{r, echo = F}
eag <-
  read_excel("eag.xlsx", sheet = "test eag")

fid <-
  read_excel("eag.xlsx", sheet = "Peak")

@@

fid_plot <- 
filled_data %>%
  dplyr::select(MeasRetTime, Area, Height) %>%
  mutate(Height = ifelse(MeasRetTime < 3.2, 0, Height)) %>%
  mutate()
  # ggplot() +
  # geom_point(aes(x = MeasRetTime, y = Height)) +
  # geom_line(aes(x = MeasRetTime, y = Height)) +
  # theme_bw()
eag_plot <-
eag %>%
  mutate(row_num = row_number()) %>%
  rename("EAD" = 'EAD 1')

ggplotly(
ggplot() +
  geom_line(data = fid_plot, aes(x = MeasRetTime, 
                                 y = Height), 
            color = "red") +
  geom_line(data = eag_plot %>%
              mutate(EAD = ifelse(row_num == 42500, -1.5, EAD),
                     EAD = ifelse(row_num == 42501, -1, EAD)), aes(x = scale_values(row_num)+0.2, 
                                 y = EAD * 100), 
            color = "blue") +

@@

# ggplotly(
#   ggplot(data = eag_plot,
#          aes(x = row_num,
#              y = EAD)) +
#     geom_line() +
#     theme_bw()
# )

stimuli <- 
eag_plot %>%
  filter(row_num >= 19220 & row_num <= 19810)
```
